Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-12 article/article.Rmd
Commit 2024-06-12 09:12

The distribution of the number of CE events as a function of OIR is shown in
Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently, there is an inverse
relation between the frequency of CE events  and OIR with an exponential-like
decline. This is expected, as the stronger the CE events become, the rarer are the
conditions favoring the occurrence of CE events. For the majority (over $60\%$) of
the CE events the OIR is below the long term average of $40\,\text{W}/\text{m}^2$,
while about $10\%$ of the events correspond to OIR larger than
$100\,\text{W}/\text{m}^2$ and up to highest value of 300 W/m^2^ .
particular atmospheric and sun conditions can
occur. This fact, is indicative to the magnitude and the probability of the expected OIRs
events over Thessaloniki. Similar distribution of CE occurrences have been reported
by @Vamvakas2020, where the magnitude of OIR were
higher due to the location of the city of Patras, $2.5^\circ$ closer to the equator.

>>>>

The distribution of the number of CE events as a function of OIR is shown in
Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently, there is an inverse
relation between the frequency of CE events  and OIR with an exponential-like
decline. This is expected, as the stronger the CE events become, the rarer are the
conditions favoring the occurrence of CE events. For the majority (over $60\%$) of
the CE events the OIR is below the long term average of
$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$,
while about $10\%$ of the events correspond to OIR larger than
$100\,\text{W}/\text{m}^2$ and up to highest value of 300 W/m^2^.
This distribution is indicative of the magnitude and the probability of the expected
CE
events over Thessaloniki. Similar distribution of CE events, occurrences have been reported
by @Vamvakas2020, where the magnitude of OIR were
higher due to the location of the city of Patras, $2.5^\circ$ closer to the equator.

### 2024-06-12 article/article.tex
Commit 2024-06-12 09:12

The distribution of the number of CE events as a function of OIR is
shown in Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently,
there is an inverse relation between the frequency of CE events and OIR
with an exponential-like decline. This is expected, as the stronger the
CE events become, the rarer are the conditions favoring the occurrence
of CE events. For the majority (over \(60\%\)) of the CE events the OIR
is below the long term average of \(40\,\text{W}/\text{m}^2\), while
about \(10\%\) of the events correspond to OIR larger than
\(100\,\text{W}/\text{m}^2\) and up to highest value of 300
W/m\textsuperscript{2} . particular atmospheric and sun conditions can
occur. This fact, is indicative to the magnitude and the probability of
the expected OIRs events over Thessaloniki. Similar distribution of CE
occurrences have been reported by \citet{Vamvakas2020}, where the
magnitude of OIR were higher due to the location of the city of Patras,
\(2.5^\circ\) closer to the equator.

>>>>

The distribution of the number of CE events as a function of OIR is
shown in Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently,
there is an inverse relation between the frequency of CE events and OIR
with an exponential-like decline. This is expected, as the stronger the
CE events become, the rarer are the conditions favoring the occurrence
of CE events. For the majority (over \(60\%\)) of the CE events the OIR
is below the long term average of \(39.9\,\text{W}/\text{m}^2\), while
about \(10\%\) of the events correspond to OIR larger than
\(100\,\text{W}/\text{m}^2\) and up to highest value of 300
W/m\textsuperscript{2}. This distribution is indicative of the magnitude
and the probability of the expected CE events over Thessaloniki. Similar
distribution of CE events, occurrences have been reported by
\citet{Vamvakas2020}, where the magnitude of OIR were higher due to the
location of the city of Patras, \(2.5^\circ\) closer to the equator.
